---
title: "TidyTuesday - Coffee Ratings"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

Working through an old (2020-07-07) [TidyTuesday posting on coffee ratings](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-07-07).

Data originally drawn from the Coffee Quality Institute, compiled [here](https://github.com/jldbc/coffee-quality-database) by James LeDoux. From the TidyTuesday repo description:

*"There is data for both Arabica and Robusta beans, across many countries and professionally rated on a 0-100 scale. All sorts of scoring/ratings for things like acidity, sweetness, fragrance, balance, etc - may be useful for either separating into visualizations/categories or for modeling/recommenders."*

Data are contained in a single file - coffee_ratings.csv - which you can pull via the tidytuesdayR package. 

```{r, eval=FALSE}

library(tidytuesdayR)

tt <- tt_load('2020-07-07')
tt$coffee_ratings

```


## Notes

After first hearing about TidyTuesday from [Michael Chow's](https://rstudio.com/resources/rstudioglobal-2021/bringing-the-tidyverse-to-python-with-siuba/) Q&A at the 2021 rstudio::global conference, I wanted to check it out for myself. Wrangling data you haven't seen before is a great exercise / helps you stay sharp. I also think this would be a great basis for a professional development event or user meetup. The TidyTuesday folks take care of a lot of the groundwork for an event organizer - finding a dataset, developing an initial description/documentation, and making it easy for users to get up and running via the "tidytuesdayR" package.

I'm also trying out ["renv"](https://rstudio.github.io/renv/articles/renv.html) for the first time (mentioned several times at rstudio::global). I'm a big fan of virtual/conda environments when using Python and getting package dependencies straightened out when sharing code across many individual users is often challenging ([Marcus Adams'](https://rstudio.com/resources/rstudioglobal-2021/not-the-app-we-deserve-the-app-we-need-putting-a-gmp-shiny-app-into-production/) riff on Dante's inferno and the "7 Circles of R Reproducibility Hell" resonated strongly)
